% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
\documentclass[
  10pt,
]{article}
\usepackage{xcolor}
\usepackage[a4paper, top=1.5cm, bottom=1.5cm, left=1.8cm,
right=1.8cm]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Source Serif 4}
  \setsansfont[]{IBM Plex Sans}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{setspace}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\pagenumbering{gobble}
\pagestyle{empty}
\usepackage{xcolor}
\definecolor{cvnavy}{HTML}{0B1F3A}
\definecolor{cvsub}{HTML}{36507A}
\usepackage{titlesec}
\titleformat{\section}{\sffamily\bfseries\fontsize{22pt}{24pt}\selectfont\color{cvnavy}}{}{0pt}{}
\titlespacing*{\section}{0pt}{0pt}{2pt}
\titleformat{\subsection}{\sffamily\bfseries\fontsize{11.5pt}{13pt}\selectfont\color{cvnavy}}{}{0pt}{\MakeUppercase}\\
{[}\{\color{cvnavy}\titlerule[0.6pt]\}{]}
\titlespacing*{\subsection}{0pt}{12pt}{4pt}
\titleformat{\subsubsection}{\sffamily\bfseries\fontsize{10.5pt}{12pt}\selectfont\color{cvnavy}}{}{0pt}{}
\titlespacing*{\subsubsection}{0pt}{8pt}{2pt}
\setlength{\parskip}{2pt}
\setlength{\parindent}{0pt}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=14pt,topsep=2pt,itemsep=1pt,parsep=0pt}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={{[}HTML{]}\{1551A8\}},
  filecolor={Maroon},
  citecolor={{[}HTML{]}\{1551A8\}},
  urlcolor={{[}HTML{]}\{1551A8\}},
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\setstretch{1.15}
\section{Marvis Osazuwa}\label{marvis-osazuwa}

{\sffamily\bfseries\fontsize{11pt}{13pt}\selectfont\color{cvsub}Analytics Engineer\,·\,Data Scientist\par}
\vspace{2pt}

Manchester, UK · marvis.osazuwa@hotmail.com · +44 7349 949871 ·
\href{https://linkedin.com/in/marvisosazuwa}{linkedin.com/in/marvisosazuwa}
· \href{https://github.com/marz1307}{github.com/marz1307} ·
\href{https://marz1307.github.io}{marz1307.github.io}

\subsection{Profile}\label{profile}

I make data trustworthy, then I make it predictive. Analytics Engineer
and Data Scientist with seven years across retail banking, mortgage
analytics, healthcare marketing, and a current Analytics Engineer role
at a SaaS company. I design dimensional models in SQL, transform with
dbt, orchestrate with Dagster, and ship ML pipelines that explain
themselves. I care about Kimball modelling, CI/CD for data, and making
the analysts and product teams downstream of me faster. UK-based, open to
UK and Germany/EU roles. UK Graduate visa (no sponsorship needed), EU Blue
Card eligible.

\subsection{Experience}\label{experience}

\subsubsection{Analytics Engineer · Force24 · Leeds, UK (Hybrid) ·
January 2026 -- April
2026}\label{analytics-engineer-force24-leeds-uk-hybrid-january-2026-april-2026}

Marketing automation SaaS. Greenfield Account Intelligence platform
built over 16 weeks for Customer Success Managers, accounts, and
stakeholders. Two-student team under technical supervision; PostgreSQL
and Angular mandated by Force24, every other tool decision mine.

\begin{itemize}
\tightlist
\item
  Owned the data layer end to end. Dagster orchestration on a VM with
  Caddy fronting it for admin authentication, custom Python extractors
  against multiple source systems, layered PostgreSQL warehouse using
  dbt across raw, staging, intermediate, and marts.
\item
  Authored every dbt model from scratch: staging views, intermediate
  business-logic tables, and curated marts (accounts, revenue, support,
  CSM metrics), with tests, documentation, and lineage.
\item
  Wired the warehouse into the FastAPI service through endpoint changes,
  Redis caching where the API was hitting the warehouse too often, and
  scheduled batch jobs.
\item
  Built the Action Tracker on the Angular frontend as the lead feature:
  CSMs create actions manually or accept smart-suggested actions, admins
  assign work, and outcomes are captured as structured
  action-context-outcome triples designed to feed a future causal-model
  layer.
\end{itemize}

\subsubsection{CRM Data Specialist · Natural Clinic · Istanbul, Türkiye
· June 2024 -- January
2025}\label{crm-data-specialist-natural-clinic-istanbul-tuxfcrkiye-june-2024-january-2025}

Healthcare marketing operation. CRM data and analytics ownership across
patient acquisition, conversion, and retention.

\begin{itemize}
\tightlist
\item
  Rebuilt the CRM data layer end to end as the single source of truth
  for sales, marketing, and clinical operations. Lead response time
  dropped 30\%; conversion rose 15\%; duplicates and data errors fell
  40\%; email engagement rose 25\%.
\item
  Designed and shipped real-time Power BI dashboards and exec-ready
  reports that replaced weekly manual spreadsheets, giving leadership
  live visibility for the first time.
\item
  Integrated the CRM with the marketing automation stack (email, SMS,
  paid funnels) and engineered customer data flows between CRM, patient
  management, and marketing tooling, eliminating three days a week of
  manual reconciliation.
\item
  Partnered daily with marketing, clinical operations, and customer
  service to translate ambiguous business questions into structured data
  models and measurable outcomes.
\end{itemize}

\subsubsection{Strategic Data Insights Analyst · Federal Mortgage Bank
of Nigeria · Abuja, Nigeria · December 2018 -- November
2019}\label{strategic-data-insights-analyst-federal-mortgage-bank-of-nigeria-abuja-nigeria-december-2018-november-2019}

Federal mortgage institution managing Nigeria's national housing fund.
Loan portfolio analytics and IT-governance reporting.

\begin{itemize}
\tightlist
\item
  Ran a data-integrity overhaul that improved core dataset accuracy by
  40\% in six months, materially reducing the risk of faulty loan
  approvals.
\item
  Built Python and SQL analytics models on top of Tableau to track loan
  repayment behaviour, lifting repayment-monitoring efficiency by 15\%
  and cutting manual data entry by 25\%.
\item
  Streamlined IT asset governance and approval workflows, cutting
  approval turnaround by 30\%.
\end{itemize}

\subsubsection{Customer Information and Service Specialist · GTBank ·
Edo, Nigeria · September 2015 -- March
2016}\label{customer-information-and-service-specialist-gtbank-edo-nigeria-september-2015-march-2016}

Early-career role at a Tier-1 African retail bank.

\begin{itemize}
\tightlist
\item
  Analysed customer interaction data to identify drop-off and friction
  points, feeding insights into cross-functional teams.
\item
  Led adoption campaigns for USSD and Internet banking, reducing
  in-branch manual transactions and shifting customers onto
  self-service.
\item
  Owned complaint resolution logging and root-cause categorisation,
  feeding monthly service-quality reporting.
\end{itemize}

\subsection{Education}\label{education}

\textbf{MSc Data Science} · University of Salford, Manchester, UK ·
January 2025 -- May 2026 Dissertation: Agentic ELT Data Platform for Customer Intelligence. Coursework
in machine learning, big data engineering, applied statistics, and
data-driven decision making.

\textbf{MSc Big Data Analytics and Management} · Bahçeşehir University,
Istanbul, Türkiye · September 2020 -- March 2023 · GPA 3.67/4.00
Master's thesis: PySpark pipeline ranking and recommending players
across five European football leagues using UEFA event data.

\textbf{BEng Computer Engineering} · University of Benin, Edo, Nigeria ·
September 2011 -- August 2017

\subsection{Selected Projects}\label{selected-projects}

\textbf{Pharma Side Effect Classification} · 2025 · NLP and Healthcare
Multi-label NLP classifier on patient-reported drug reviews. RoBERTa
fine-tuned for therapeutic-area and side-effect tagging. Topic modelling
with LDA, sentiment analysis with TF-IDF baselines, model selection
across precision-recall trade-offs.

\textbf{Equity Forecasting} · 2025 · Financial Time Series End-to-end R
analysis package for univariate equity forecasting on 5,124 daily NYSE
observations. ARIMA, seasonal ARIMA, and ETS through a MODEL\_REGISTRY
pattern. Formal residual diagnostics (Ljung-Box, Shapiro-Wilk) and
stationarity tests (ADF, KPSS) combined into a single decision rule.

\textbf{Football Player Scouting at Scale} · MSc Thesis · 2023 · Big
Data and Sports Analytics Distributed PySpark pipeline ranking and
recommending 500+ footballers across La Liga, Serie A, Premier League,
Bundesliga, and Ligue 1 using UEFA event data. Engineered KPIs capturing
on-ball and off-ball contribution. Published thesis, public codebase.

\textbf{Steam Games Recommender} · Side Project · 2024 · Recommender
Systems PySpark + ALS recommender on the Steam 200k implicit-feedback
dataset. Distributed training with Grid Search across CrossValidator and
TrainValidationSplit. Full experiment tracking in MLflow on Databricks.

\subsection{Technical Skills}\label{technical-skills}

\textbf{Languages:} SQL · Python · R · PySpark · T-SQL · Bash
\textbf{Warehousing:} PostgreSQL · Snowflake · BigQuery · Databricks ·
SQL Server \textbf{Transformation \& Orchestration:} dbt · Dagster ·
Apache Spark · Airflow \textbf{Service Layer:} FastAPI · REST APIs ·
Docker · Caddy \textbf{ML \& Statistics:} scikit-learn · XGBoost · SHAP
· MLflow · RoBERTa · ARIMA · NLP · Sentiment Analysis · TF-IDF · LDA
\textbf{BI \& Visualisation:} Power BI · Tableau · Looker
\textbf{Cloud:} AWS · GCP · Azure \textbf{Source Control \& Tooling:}
Git · GitHub · GitHub Actions · pytest

\subsection{Languages}\label{languages}

\textbf{English:} Native or bilingual proficiency · \textbf{German:}
Limited working proficiency, actively improving toward B1

\subsection{Certifications}\label{certifications}

Engineer Data for Predictive Modeling with BigQuery ML (Google Cloud) ·
Python for Data Science, AI \& Development (Coursera) · Generative AI for Business
Leaders (Coursera) · Enterprise Design Thinking Practitioner (IBM) ·
Tableau for Data Scientists (LinkedIn Learning) · Statistics Foundations
1--4 (LinkedIn Learning) · R for Data Science (LinkedIn Learning)

\end{document}
